---
title: "Assignment7Output"
author: "43141 (Sahil Naphade)"
date: "17/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the libraries
```{r}
library("arules")
library('arulesViz')
library('tidyverse')
library('knitr')
library('lubridate')
library('plyr')
library('dplyr')
library('datasets')
```

# Read the dataset and inpect
```{r}
pd <- read.transactions("./groceries.csv",sep=',', header = F)
inspect(pd[1:10,])
```
# Summary of Dataset
```{r}
summary(pd)
```

# Plotting various graphs for the dataset
## 1. Relative frequency graph
```{r}
itemFrequencyPlot(pd, support = .001, topN = 50, col="lightgreen", xlab = "Item name", 
                  ylab = " Frequency (relative)", main = "Top 50 items with 0.001 support (relative)")
```
### This graph shows the top 50 products which have appeared in at least 0.1% of total records
#### We can see that "Whole milk" is most sold product, followed by "other vegetables", "Buns", "Soda" and "Yogurt"

## 2. Absolute frequency graph
```{r}
itemFrequencyPlot(pd, topN = 15, col="lightblue", xlab = "Item name", type = "absolute", 
                  ylab = " Frequency (Absolute)", main = "Top 15 items (absolute frequency)")
```

# Defining Apriori rules for support = 0.001 and Confidence = 0.8 with minimum length = 2
```{r}
pd_rules = apriori(pd, parameter = list(support = 0.001, confidence = 0.8, minlen = 2))
summary(pd_rules, limit = 3)
```
## Checking the rules as per "lift"
```{r}
inspect(sort(pd_rules, by="lift"))
```
## Plotting various graphs for the rules
```{r}
plot(pd_rules)
```
```{r}
plot(pd_rules,method="grouped", jitter = 0)
```
```{r}
plot(pd_rules,method="graph")
```
```{r}
plot(pd_rules, method="graph", control=list(layout=igraph::in_circle()))
```
# Sorting the rules by confidence value
```{r}
rules = sort(pd_rules, by = "confidence")
options(digits = 2)
inspect(rules)
```

# removing redundant rules
```{r}
inspect(rules[is.redundant(rules)])
rules = rules[!is.redundant(rules)]
inspect(rules[1:5])
```
# Rules for "Whole milk" (Most bought product)
```{r}
rules1 = apriori(pd, parameter = list(support = 0.001, confidence = 0.8, minlen = 2),
                appearance = list(default = "lhs", rhs = "whole milk"))
options(digits = 2)
inspect(rules1)
```
# Plotting graphs for the new rules
```{r}
# Only for interactive sessions
# plot(rules1, method = "graph", engine = "interactive")
```
```{r}
plot(rules1, method = "paracoord")
```
```{r}
plot(rules1, method = "matrix", control = list(reorder = "none"))
```
```{r}
plot(rules1, jitter = 0)
```

