---
title: "Principal Component Analysis in R"
author: "43141 (Sahil Naphade)"
date: "02/12/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Reading the Wine dataset and checking
```{r}
setwd("E:/College/CL7/Assignment12")
winedf <- read.csv("../Datasets/wine.csv")

head(winedf)

```

# Calculate Correlation of all attributes
```{r}
cor_mat <- cor(winedf[, -1])
cor_mat

``` 
### We see that alcohol and Proline, alcohol and Color.int has fairly high correlation.
### Similarly, Phenols with Proanth, and Flavanoids with Proanth has high correlation.
### Flavanoids and nonflavanoids phenols has high negative correlation.

# Checking the principal components of the dataset.
```{r}
WPCA <- princomp(winedf[, -1], cor = T, scores = T, covmat = NULL)
summary(WPCA)
```
## Plot the WPCA graph
```{r}
plot(WPCA)
```

## (component coefficients) correlation coefficients between variables(rows) and factors(columns)
```{r}
loadings(WPCA)
```

### Checking the attributes of the Principal Component Analysis
```{r}
attributes(WPCA)
```

### Plotting various graphs and scree graph to check the variation of information in the variables/components.
```{r}
plot(WPCA, t='l')
```
```{r}
screeplot(WPCA, type="line", main="Scree plot")
```
```{r}
biplot(WPCA)
```
## Check the score of PCA
```{r}
WPCA$scores[1:10, 1]
```

