---
title: "CL7 Assignment5"
author: "43141 (Sahil Naphade)"
date: "10/10/2020"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Adding the libraries and reading the file
```{r}
library("lattice")
library("Metrics")
library("DAAG")
library("leaps")
library("ISLR")
#df<-df("advertising.csv")
df <- read.csv("./advertising.csv")
head(df)
dim(df) # Dimensions of the dataset
```
Divide the dataset into training and testing
```{r}
train_dataset=df[1:120,]
head(train_dataset)

test_dataset=df[121:200,]
head(test_dataset)
```

## Columns for binding for predictioin
```{r}
S=cbind("TV","Newspaper","Radio")
```
# Linear regression using Least Square method on TV
```{r}
TV1=lm(Sales~TV,data=train_dataset)
TV1
  # Display the attributes of Linear regression of TV
attributes(TV1)
TV1$coefficients[1]
TV1$coefficients[2]
```
# Linear regression using Least Square method on Radio
```{r}
Radio1=lm(Sales~Radio,data=train_dataset)
Radio1
  # Display the attributes of Linear regression of Radio
attributes(Radio1)
Radio1$coefficients[1]
Radio1$coefficients[2]
```
# Linear regression using Least Square method on Newspapers
```{r}
# Linear regression using Least Square method on Newspapers
Newspaper1=lm(Sales~Newspaper,data=train_dataset)
Newspaper1
  # Display the attributes of Linear regression of Radio
attributes(Newspaper1)
Newspaper1$coefficients[1]
Newspaper1$coefficients[2]
```

Plotting graphs of parts of dataset vs sales
```{r}
# 1. With TV
plot(train_dataset$Sales~train_dataset$TV,xlab="TV",ylab = "Sales")
abline(TV1, col="red")
```

```{r}
# 2. With Radio
plot(train_dataset$Sales~train_dataset$Radio,xlab="Radio",ylab = "Sales")
abline(Radio1, col="blue")
```

```{r}
# 3. with Newspaper
plot(train_dataset$Sales~train_dataset$Newspaper,xlab="Newspaper",ylab="Sales")
abline(Newspaper1, col="green")
```

```{r}
summary(TV1)

#tidy(TV1)

Tvp=predict(TV1,train_dataset)
Radiop=predict(Radio1,train_dataset)
Newspaperp=predict(Newspaper1,train_dataset)

# Predict on the test data-set
Tvt=predict(TV1,test_dataset)
Radiot=predict(Radio1,test_dataset)
Newspapert=predict(Newspaper1,test_dataset)
```
Finding mean square error on Training dataset
```{r}
TVtrain_mse=mse(train_dataset$Sales,Tvp)
TVtrain_mse

Radiotrain_mse=mse(train_dataset$Sales,Radiop)
Radiotrain_mse

Newspapertrain_mse=mse(train_dataset$Sales,Newspaperp)
Newspapertrain_mse
```

Finding mean square error on testing dataset
```{r}
TVtest_mse=mse(test_dataset$Sales,Tvt)
TVtest_mse

Radiotest_mse=mse(test_dataset$Sales,Radiot)
Radiotest_mse

Newspapertest_mse=mse(test_dataset$Newspaper,Newspapert)
Newspapertest_mse
```
Combines the arguments to form a vector
```{r}
TrainMSE=c(TVtrain_mse,Radiotrain_mse,Newspapertrain_mse)  
TrainMSE

TestMSE=c(TVtest_mse,Radiotest_mse,Newspapertest_mse)
TestMSE
```
```{r}
barplot(TrainMSE,width = 0.02,xlab="data",ylab="error",main="Training Error")
```
```{r}
barplot(TestMSE,width=0.02,xlab = "data",ylab="error",main="Testing Error")
```
# Using Subset selection method
```{r}
regfit_full = regsubsets(Sales~., data= test_dataset)
reg_summary = summary(regfit_full)
reg_summary$rsq
```
Set up a 2x2 grid so we can look at 4 plots at once
```{r}
par(mfrow = c(2,2))
plot(reg_summary$rss, xlab = "Number of Variables", ylab = "RSS", type = "l")
plot(reg_summary$adjr2, xlab = "Number of Variables", ylab = "Adjusted RSq", type = "l")
# We will now plot a red dot to indicate the model with the largest adjusted R^2 statistic.
# The which.max() function can be used to identify the location of the maximum point of a vector
adj_r2_max = which.max(reg_summary$adjr2) # 11

# The points() command works like the plot() command, except that it puts points 
# on a plot that has already been created instead of creating a new plot
points(adj_r2_max, reg_summary$adjr2[adj_r2_max], col ="red", cex = 2, pch = 20)
```
We'll do the same for C_p and BIC, this time looking for the models with the SMALLEST statistic
```{r}
plot(reg_summary$cp, xlab = "Number of Variables", ylab = "Cp", type = "l")
cp_min = which.min(reg_summary$cp) # 10
points(cp_min, reg_summary$cp[cp_min], col = "red", cex = 2, pch = 20)
```

```{r}
plot(reg_summary$bic, xlab = "Number of Variables", ylab = "BIC", type = "l")
bic_min = which.min(reg_summary$bic) # 6
points(bic_min, reg_summary$bic[bic_min], col = "red", cex = 2, pch = 20)
```